The one characterizing the parental care stages

### 2019-10-16 docs/ms1-charactization.Rmd
typos
new pca plots

## Fig 2: Prolactin fluctuates the most and peaks near hatch in males and females

@@

## Figure 3: General RNAseq pattern, tissue > sex > parental stage

@@

![](../figures/limma/plotMDS-colored-1.png)

## Figure 4: model showing ability to predict non-parental, egg care, and nestling care

_redo color scheme, fix titles_

@@

>>>>

## Fig 2: Of the hormones measured, prolactin fluctuates the most and peaks near hatch in males and females

@@

## Figure 3: PCA

@@

![](../figures/pca/pca-1.png)

## Figure 4: LDA

![](../figures/sexes/LDA-4.png)

@@

https://osf.io/g3kc5/
